maze-dataset

### 2025-03-30 docs/paper/paper.tex
paper stuff

\begin{figure} 
  \begin{minipage}{5in}
    \input{docs/paper/diagram/diagram.tikz} 
  \end{minipage}
  \caption{Usage of maze-dataset. We create a `MazeDataset` from a `MazeDatasetConfig`. This contains `SolvedMaze` objects which can be converted to and from a variety of formats. Code in the image contains clickable links to \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html}{documentation}. A variety of generated examples can be viewed \href{https://understanding-search.github.io/maze-dataset/examples/maze_examples.html}{here}.}
  \label{fig:diagram}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:visualoutputs}{%
\centering
\includegraphics{docs/paper/figures/output-fmts.pdf}
\caption{Various output formats. Top row (left to right): ASCII diagram,
rasterized pixel grid, and advanced display.}\label{fig:visualoutputs}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:e2hraster}{%
\centering
\includegraphics[width=0.3\textwidth,height=\textheight]{docs/paper/figures/maze-raster-input-target.pdf}
\caption{Input is the rasterized maze without the path marked (left),
and provide as a target the maze with all but the correct path removed.
Configuration options exist to adjust whether endpoints are included and
if empty cells should be filled in.}\label{fig:e2hraster}
}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{docs/paper/figures/outputs-tokens-colored.tex}
\caption{Example text output format with token regions highlighted.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{docs/paper/figures/TokenizerElement_structure.pdf}
\caption{Nested internal structure of \texttt{\_TokenizerElement}
objects inside a typical \texttt{MazeTokenizerModular} object.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth,height=\textheight]{docs/paper/figures/gridsize-vs-gentime.pdf}
\caption{Plots of maze generation time. Generation time scales
exponentially with maze size for all algorithms (left). Generation time
does not depend on the number of mazes being generated, and there is
minimal overhead to initializing the generation process for a small
dataset (right). Wilson's algorithm is notably less efficient than
others and has high variance. Note that for both plots, values are
averaged across all parameter sets for that algorithm, and
parallelization is disabled.}
\end{figure}

>>>>

\begin{figure} 
  \begin{minipage}{5in}
    \input{diagram/diagram.tikz} 
  \end{minipage}
  \caption{Usage of maze-dataset. We create a `MazeDataset` from a `MazeDatasetConfig`. This contains `SolvedMaze` objects which can be converted to and from a variety of formats. Code in the image contains clickable links to \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html}{documentation}. A variety of generated examples can be viewed \href{https://understanding-search.github.io/maze-dataset/examples/maze_examples.html}{here}.}
  \label{fig:diagram}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:visualoutputs}{%
\centering
\includegraphics{figures/output-fmts.pdf}
\caption{Various output formats. Top row (left to right): ASCII diagram,
rasterized pixel grid, and advanced display.}\label{fig:visualoutputs}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:e2hraster}{%
\centering
\includegraphics[width=0.3\textwidth,height=\textheight]{figures/maze-raster-input-target.pdf}
\caption{Input is the rasterized maze without the path marked (left),
and provide as a target the maze with all but the correct path removed.
Configuration options exist to adjust whether endpoints are included and
if empty cells should be filled in.}\label{fig:e2hraster}
}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/outputs-tokens-colored.tex}
\caption{Example text output format with token regions highlighted.}
\end{figure}

@@

\begin{figure}
    \centering
    \input{figures/TokenizerElement_structure.tikz}
    \caption{Nested internal structure of \texttt{\_TokenizerElement} objects inside a typical \texttt{MazeTokenizerModular} object.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth,height=\textheight]{../benchmarks/figures/gridsize-vs-gentime.pdf}
\caption{Plots of maze generation time. Generation time scales
exponentially with maze size for all algorithms (left). Generation time
does not depend on the number of mazes being generated, and there is
minimal overhead to initializing the generation process for a small
dataset (right). Wilson's algorithm is notably less efficient than
others and has high variance. Note that for both plots, values are
averaged across all parameter sets for that algorithm, and
parallelization is disabled.}
\end{figure}

\begin{figure}
\centering
\includegraphics{../benchmarks/figures/n_mazes-vs-gentime.pdf}
\caption{Maze size vs generation time}
\end{figure}
